### 2022-01-11 paper/paper.tex
rewrite FMA contraction part

As demonstrated in Section~\ref{sec:performance-comparison},
Julia is not generically slower than traditional high-performance programming
languages like C, C++, and Fortran. A minor exception is due to
Julia being built on top of LLVM, which does not perform the same optimizations as other
C/C++/Fortran compilers. In particular, most LLVM frontends (including Julia) do
not enable fused multiply-add (FMA) contraction by default, while GCC and Intel
compilers do. Thus, one must opt-in to these optimizations explicitly.
Relying on Julia's code manipulation techniques, this can be achieved with the macro
\lstinline{@muladd}\footnote{\url{https://github.com/SciML/MuladdMacro.jl}},
which makes it convenient to use Julia's function \lstinline{muladd}\footnote{\url{https://docs.julialang.org/en/v1/base/math/\#Base.muladd}}.

>>>>

As demonstrated in Section~\ref{sec:performance-comparison},
Julia is not generically slower than traditional high-performance programming
languages like C, C++, and Fortran. A minor exception in the context of scientific
computing relying on floating point operations is that Julia does not enable
fused multiply-add (FMA) contraction by default, while GCC and Intel compilers
do\footnote{An interesting coincidence is that not only Julia but most LLVM-based
frontends tend not to enable FMA contraction by default.}.
Thus, one must opt-in to these optimizations explicitly.
Relying on Julia's code manipulation techniques, this can be achieved with the macro
\lstinline{@muladd}\footnote{\url{https://github.com/SciML/MuladdMacro.jl}},
which makes it convenient to use Julia's function \lstinline{muladd}\footnote{\url{https://docs.julialang.org/en/v1/base/math/\#Base.muladd}}.
